### 2023-09-01 paper/sec-dis-pseudodata.tex
minor wording changes. nu-flux description

In our calculation we assume the central values of the neutrino
fluxes provided by~\cite{Kling:2021gos} and used
for the FPF simulations in~\cite{Feng:2022inv}.
%
The bin-by-bin integrated event yields in Eq.~(\ref{eq:event_yields}) are
obtained by convoluting the incoming neutrino fluxes, for a given acceptance
of the target detector, with the corresponding neutrino differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Binned event yields are evaluated using
\begin{equation}
  \label{eq:event_yields_calculation}
   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,
\end{equation}
with $n_T$ is the nucleon density of the target detector material, $L_T$ its
length and ${\cal A}(x,Q^2,E_{\nu})$ is an acceptance factor which takes the form of a
step function and accounts for the experimental acceptances
in $E_\ell$, $\theta_\ell$, and $E_h$
listed in Table~\ref{tab:FPF_experiments}.
%
The incoming neutrino fluxes, which account for the geometry
and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector,
are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
%
%We have verified that the differential event yield calculation
%implemented in Eq.~(\ref{eq:event_yields_calculation}), when extrapolated to a single bin
%covering the full detector acceptance,
%is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv} once DIS cuts are imposed and detector acceptances are accounted for.
%

@@

For each independent source of experimental systematic uncertainty, we hence
quantify its impact at the event yield level.
%
In order to determine these bin-by-bin systematic errors,
we extend the calculation delineated in Sec.~(\ref{sec:pseudo-data_generation}) as follows.
%{\color{blue} [MF: I don't think this faser example is necessary]}
%Let us consider for illustrative purposes the FASER${\nu}$2 detector.
%
%From Table~\ref{tab:FPF_experiments} we know that its
%acceptance parameters and reconstruction performance are specified by:
%\bea
%E_\ell \ge 100~{\rm GeV} \, , \quad \theta_\ell \le \tan^{-1}(0.025)\, , \qquad\\
%\delta E_\ell \sim 30\% \, 
 %\quad \delta E_h \sim 30\% \, ,
 %\quad \delta\theta_\ell \sim 0.06~{\rm mrad} \, . 
%\label{eq:fasernu2systematic_errors}
%\eea
%To translate these uncertainties in $\delta E_\ell$, $\delta E_h $,
To translate uncertainties in $\delta E_\ell$, $\delta E_h $
and $\delta\theta_\ell$ into systematic errors associated to the event yields, 
\be
\label{eq:event_yields_systematic_error}
\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} \, ,\quad
\delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(i)}
\, ,\quad
\delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(i)} \, ,\qquad i=1,\ldots,N_{\rm bin} \, ,
\ee
we first generate a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
composed by $N_{\rm mc} \approx 10^7$ samples and determine the assignment of each event
to a point in the $\lp x,Q^2,E_{\nu}\rp$ space.
%
By comparing $\mathcal{D}_0$ with the number of events as calculated by Eq.~(\ref{eq:event_yields_calculation}), 
we can normalize the sampled distribution with a factor $\hat{n}$ to reproduce the expected yield.

We then take each event in $\mathcal{D}_0$ and smear it with Gaussian distributions whose variances are given by Table~\ref{tab:FPF_experiments} to produce new samples $\mathcal{D}_k$. The smeared samples are subjected to the same DIS cuts from Eq.~(\ref{eq:DISconditions}) and acceptances from Table~\ref{tab:FPF_experiments}. The bin assignment of the events in the smeared samples $\mathcal{D}_k$ will in general be different from those of the baseline sample.

%
We take the uncertainty associated
to a given systematic source, say $\delta E_\ell$,
to be the mean of the absolute difference between the number of events in this bin for the smeared samples, normalized by $\hat{n}$, and the central prediction for the number of events
$ N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{eq:event_yields_calculation}):
\be
\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} =\la \Big|  \hat{n}\times{N}^{(i)}_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big|\ra \, .
\ee

@@

In general, systematic uncertainties associated to the hadronic final state energy $E_h$ appear to be the largest,
reaching up to $\sim 90\%$ for some experiments.
%
We recall that measurement of $E_h$ in addition to the leptonic variables is required to
fix the incoming neutrino energy $E_\nu$, which is different in each event unlike
the case of neutral-current scattering.
%
The uncertainties associated to the charged-lepton energy $E_\ell$ and scattering angle $\theta_\ell$ range
between a few percent up to 20\% in the  baseline scenario listed in Table~\ref{tab:FPF_experiments}.
%
For the $\delta \theta_\ell$ variations, they are smallest in the large-$x$ region
for $x\gsim 0.1$, where they are at the few-percent level typically.
%
Statistical uncertainties are subdominant in most of the bins and are below the 10\% level,
specially at large-$x$ which is the kinematic region benefitting from the largest event rates.

@@

The end result of the procedure is an estimate of statistical and systematic uncertainties
for each bin of the measurement, from which a experimental covariance matrix can be constructed as
\be
\label{eq:covmat_definition}
   {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
   + \sum_{k=1}^{n_{\rm sys}}\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp \lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(j)} \rp
   \, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
 \ee
  and the same for the associated correlation
 matrix of the measurement
 \be
\label{eq:corrmat_definition}
 \rho_{ij} =  \frac{{\rm cov}_{ij}}{\sqrt{ {\rm cov}_{ii} }\sqrt{ {\rm cov}_{jj} } } \, . 
 \ee
 The relative covariance matrix, $ {\rm cov}_{ij}/( N_{\rm ev}^{(i)}N_{\rm ev}^{(j)})$, is
 independent of the considered observable and would also apply
 for the double-differential cross-sections Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) which are related to the event yields by a constant prefactor.

>>>>

In our calculation we assume the central values of the neutrino
fluxes provided by~\cite{Kling:2021gos} and used
for the FPF simulations in~\cite{Feng:2022inv}.
%
The bin-by-bin integrated event yields in Eq.~(\ref{eq:event_yields}) are
obtained by convoluting the incoming neutrino fluxes, for a given acceptance
of the target detector, with the corresponding neutrino differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Binned event yields are evaluated using
\begin{equation}
  \label{eq:event_yields_calculation}
   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) {\cal A}(x,Q^2,E_{\nu}) dQ^2 dx dE_{\nu} \, ,
\end{equation}
with $n_T$ is the nucleon density of the target detector material, $L_T$ its
length and ${\cal A}(x,Q^2,E_{\nu})$ is an acceptance factor which takes the form of a
step function and accounts for the experimental acceptances
in $E_\ell$, $\theta_\ell$, and $E_h$
listed in Table~\ref{tab:FPF_experiments}.
%
The incoming neutrino fluxes, which account for the geometry
and neutrino pseudo-rapidity $\eta_\nu$ coverage of the considered detector,
are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$~\cite{Kling:2021gos}. The neutrino flux takes into account both the prompt component associated with neutrinos from charmed hadron decay as well as a displaced component from light hadron decays. The prompt component was simulated at NLO using \textsc{POWHEG}~\cite{Nason:2004r,Frixione:2007vwx,Alioli:2010xd} and \textsc{Pythia}~\cite{Sjostrand:2014zea, Bierlich:2022pfr} for the parton shower and hadronization, and the displaced component was simulated with \textsc{Epos-Lhc}~\cite{Pierog:2013ria}. In addition to the updated charmed hadron production, the neutrino flux from Ref.~\cite{Kling:2021gos} was also updated for $\sqrt{s} = 13.6~{\rm TeV}$.

@@

For each independent source of experimental systematic uncertainty, we hence
quantify its impact at the event yield level.
%
In order to determine these bin-by-bin systematic errors,
we extend the calculation delineated in Sec.~(\ref{sec:pseudo-data_generation}) as follows.
%{\color{blue} [MF: I don't think this faser example is necessary]}
%Let us consider for illustrative purposes the FASER${\nu}$2 detector.
%
%From Table~\ref{tab:FPF_experiments} we know that its
%acceptance parameters and reconstruction performance are specified by:
%\bea
%E_\ell \ge 100~{\rm GeV} \, , \quad \theta_\ell \le \tan^{-1}(0.025)\, , \qquad\\
%\delta E_\ell \sim 30\% \, 
 %\quad \delta E_h \sim 30\% \, ,
 %\quad \delta\theta_\ell \sim 0.06~{\rm mrad} \, . 
%\label{eq:fasernu2systematic_errors}
%\eea
%To translate these uncertainties in $\delta E_\ell$, $\delta E_h $,
To translate uncertainties in $\delta E_\ell$, $\delta E_h $
and $\delta\theta_\ell$ into systematic errors associated to the event yields, 
\be
\label{eq:event_yields_systematic_error}
\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} \, ,\quad
\delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(i)}
\, ,\quad
\delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(i)} \, ,\qquad i=1,\ldots,N_{\rm bin} \, ,
\ee
we first generate a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
composed by $N_{\rm mc} \approx 10^7$ samples and determine the assignment of each event
to a point in the $\lp x,Q^2,E_{\nu}\rp$ space.
%
By comparing $\mathcal{D}_0$ with the number of events as calculated by Eq.~(\ref{eq:event_yields_calculation}), 
we can normalize the sampled $\mathcal{D}_0$ distribution with a factor $\hat{n}$ to reproduce the expected yield.

We then take each event in $\mathcal{D}_0$ and smear it with Gaussian distributions whose variances are given by Table~\ref{tab:FPF_experiments} to produce a set of new samples $\{\mathcal{D}_k\}$. The smeared events are subjected to the same DIS cuts from Eq.~(\ref{eq:DISconditions}) and acceptances from Table~\ref{tab:FPF_experiments}. The bin assignment of the events in the smeared samples $\mathcal{D}_k$ will in general be different from those of the baseline sample $\mathcal{D}_0$.

%
We take the uncertainty associated
to a given systematic source, say $\delta E_\ell$,
to be the mean of the absolute difference between the number of events in this bin for the smeared samples $\{\mathcal{D}_k\}$ normalized by $\hat{n}$, and the central prediction for the number of events
$ N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{eq:event_yields_calculation}):
\be
\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} =\la \Big|  \hat{n}\times{N}^{(i)}_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big|\ra \, .
\ee

@@

For the experiments which use a Tungsten target, the systematic uncertainties associated to the final state energies $E_\ell$, $E_h$ are comparable and are typically $\sim 10\%$ and range from $1\%$ to  ${\cal O}(1)$ across bins. The uncertainties associated with $\theta_\ell$ are typically at or well below $1\%$ for these experiments, which can be attributed to the high spatial resolution. 
%
On the other hand, for the FLArE-10(0) experiment, uncertainties associated with the scattering angle $\theta_\ell$ dominate at $\sim 40\%$ ranging from a few percent to ${\cal O}(1)$. Whereas the uncertainties associated with final state energy resconstruction are $\sim 10\%$ and range from $\lesssim 1\%$ to $\sim 80\%$.
%
For all experiments, statistical uncertainties are subdominant in most of the bins and are below the 10\% level,
especially at large-$x$ which is the kinematic region benefitting from the largest event rates.

@@

The end result of the procedure is an estimate of statistical and systematic uncertainties
for each bin of the measurement, from which an experimental covariance matrix can be constructed as
\be
\label{eq:covmat_definition}
   {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
   + \sum_{k=1}^{n_{\rm sys}}\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp \lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(j)} \rp
   \, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
 \ee
  and the same for the associated correlation
 matrix of the measurement
 \be
\label{eq:corrmat_definition}
 \rho_{ij} =  \frac{{\rm cov}_{ij}}{\sqrt{ {\rm cov}_{ii} }\sqrt{ {\rm cov}_{jj} } } \, . 
 \ee
 The relative covariance matrix, $ {\rm cov}_{ij}/( N_{\rm ev}^{(i)}N_{\rm ev}^{(j)})$, is
 independent of the considered observable and would also apply
 for the double-differential cross-sections Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) which are related to the event yields by a constant prefactor.
